

```{r}
```{r setup, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)

# ---- Path to the Clean2 RData you saved ----
in_dir <- "C:/Users/rchhajed/OneDrive - Nexus365/Tropical Medicine - IDDO - COVID19/COVID19 LMR 2025/Cov_Main/data"

# Option A: load the latest file matching your naming pattern
rdata_in <- list.files(in_dir, pattern = "^covid_lmr_clean4_\\d{8}\\.RData$", full.names = TRUE)
stopifnot(length(rdata_in) >= 1)
rdata_in <- rdata_in[which.max(file.info(rdata_in)$mtime)]

load(rdata_in)

# Expect these to exist from Clean1/Clean2
stopifnot(exists("study_table"))
stopifnot(exists("country_table"))
stopifnot(exists("arm_table"))
stopifnot(exists("pharma_table"))

cat("Loaded:", basename(rdata_in), "\n")
cat("Unique studies (study_table):", n_distinct(study_table$st_reg_id), "\n")


clean_id <- function(x) str_to_lower(str_trim(as.character(x)))

parse_dmy_safe <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "na", "n/a", "unknown", "-99")] <- NA
  suppressWarnings(dmy(x))
}

study_table <- study_table %>%
  mutate(
    st_reg_id = clean_id(st_reg_id),
    reg_date  = parse_dmy_safe(st_reg_date)
  )

country_table <- country_table %>%
  mutate(st_reg_id = clean_id(st_reg_id))

arm_table <- arm_table %>%
  mutate(st_reg_id = clean_id(st_reg_id))

pharma_table <- pharma_table %>%
  mutate(
    st_reg_id = clean_id(st_reg_id),
    reg_date  = parse_dmy_safe(st_reg_date)
  )
```

```{r}
study_table<-study_table %>%
  mutate(era = case_when(
    reg_date < as.Date("2021-05-26") ~ "Pre-paper (to May 2021)",
    reg_date < as.Date("2023-05-05") ~ "Mid-pandemic (May 2021–May 2023)",
    TRUE                             ~ "Post-PHEIC (May 2023 onwards)"
  ))


# ── SECTION 5: Geographic analysis (country_table) ────────────────────────────

# 5.1 Country_table already has trial-country rows with income_group
geo_summary <- country_table %>%
  filter(st_reg_id %in% cohort_ids) %>%  # Only cohort trials
  count(era = study_table$era[match(st_reg_id, study_table$st_reg_id)],  # Merge era
        country_std, income_group, name = "n_countries") %>%
  group_by(era, country_std, income_group) %>%
  summarise(n_trials = sum(n_countries), .groups = "drop") %>%
  filter(!is.na(income_group))

# Better: direct join for era
geo_data <- country_table %>%
  inner_join(study_table %>% select(st_reg_id, era), by = "st_reg_id") %>%
  filter(st_reg_id %in% cohort_ids) %>%
  count(era, country_std, income_group, name = "n_trial_countries")

# QC
geo_data %>% count(era, income_group)


# ── FIG 10: Top 10 countries (HIGH→LOW ORDER within ggplot) ───────────────────
top10_countries <- geo_data %>%
  filter(!is.na(country_std)) %>%
  group_by(era) %>%
  slice_max(n_trial_countries, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  # Create explicit ranking for perfect ordering
  group_by(era) %>%
  mutate(rank = row_number()) %>%
  ungroup() %>%
  mutate(
    # Order: era + rank (highest first)
    country_ordered = reorder(country_std, -rank)
  )

fig10 <- ggplot(top10_countries, aes(y = country_ordered, x = n_trial_countries, 
                                    fill = income_group)) +
  geom_col(position = "stack", alpha = 0.9, width = 0.75) +
  facet_wrap(~era, scales = "free_y", ncol = 1) +
  scale_fill_manual(values = c(
    "High income" = "#1f77b4",
    "Upper middle income" = "#2ca02c", 
    "Lower middle income" = "yellow3",
    "Low income" = "orange1"
  )) +
  labs(title = "Top 10 Countries by Registration Era",
       x = "Number of Trials", y = "Country") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold"))

fig10


# ── FIG 12: Income stacked (era chronological) ────────────────────────────────
era_order <- c("Pre-paper (to May 2021)", 
               "Mid-pandemic (May 2021–May 2023)", 
               "Post-PHEIC (May 2023 onwards)")

# ── FIG 12: Income composition as 3 PIE CHARTS ────────────────────────────────
fig12_data <- geo_data %>%
  filter(!is.na(income_group)) %>%
  count(era, income_group, wt = n_trial_countries, name = "trials") %>%
  group_by(era) %>%
  mutate(pct = trials / sum(trials)) %>%
  ungroup()

# Prettier colors
pie_colors <- c(
  "High income" = "skyblue3",        # Bright blue
  "Upper middle income" = "skyblue4", # Vibrant orange
  "Lower middle income" = "darkgreen", # Fresh green  
  "Low income" = "darkred"           # Strong red
)

fig12 <- fig12_data %>%
  ggplot(aes(x = "", y = pct, fill = income_group)) +
  geom_col(width = 1, position = position_stack()) +
  geom_text(aes(label = scales::percent(pct, accuracy = 1)), 
            position = position_stack(vjust = 0.5),
            color = "white", size = 5, fontface = "bold") +
  coord_polar("y", start = 0) +
  facet_wrap(~era, ncol = 3) +
  scale_fill_manual(values = pie_colors) +
  labs(title = "Geographic Representation by Era") +
  theme_void(base_size = 14) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 13),
    legend.text = element_text(size = 12),
    strip.text = element_text(face = "bold", size = 14, hjust = 0.5),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 16)
  ) +
  guides(fill = guide_legend(nrow = 1))

fig12


```

```{r}
# ── Interventions by Income Group + Era (3 panels) ────────────────────────────
drug_geo_era <- study_drug %>%
  left_join(country_table %>% 
              select(st_reg_id, country_std, income_group),
            by = "st_reg_id") %>%
  inner_join(study_table %>% select(st_reg_id, era), by = "st_reg_id") %>%
  filter(!is.na(income_group), 
         !is.na(broad_cat_display),
         st_reg_id %in% cohort_ids)

# Summary table
drug_summary <- drug_geo_era %>%
  count(era, income_group, broad_cat_display, sort = TRUE)



# Use your drug_summary (already perfect!)
# Top 10 interventions OVERALL per era (not per income)
top_per_era <- drug_summary %>%
  group_by(era) %>%
  slice_max(n, n = 10, with_ties = FALSE) %>%
  ungroup()

# FIG 13: Era | Intervention | Income breakdown
fig13 <- ggplot(top_per_era, 
                aes(x = reorder(broad_cat_display, n), 
                    y = n, fill = income_group)) +
  geom_col(position = "dodge", alpha = 0.85, width = 0.9) +
  facet_wrap(~era, scales = "free_x", ncol = 1) +
  coord_flip() +
  scale_fill_manual(values = c(
    "High income" = "steelblue",
    "Upper middle income" = "steelblue4", 
    "Lower middle income" = "yellow3",
    "Low income" = "orange"
  )) +
  labs(title = "FIG 13: COVID Interventions by Era & Income Group",
       subtitle = "Top 10 categories per era | Multi-national trials in all locations",
       x = "Intervention Category", y = "# Drug-Trial-Country Registrations") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold", size = 13),
        axis.text.y = element_text(size = 10))

fig13


```


```{r}
# ── FIXED: Global Top 10 interventions (consistent across eras) ───────────────
global_top10 <- drug_summary %>%
  count(broad_cat_display, wt = n, name = "total_n") %>%
  slice_max(total_n, n = 7) %>%
  arrange(desc(total_n)) %>%
  mutate(order_rank = row_number()) %>%
  pull(broad_cat_display)

# Filter + explicit ordering
plot_data <- drug_summary %>%
  filter(broad_cat_display %in% global_top10) %>%
  mutate(cat_ordered = factor(broad_cat_display, 
                             levels = rev(global_top10)))

# PLOT - explicit factors = no reorder errors
fig13_fixed <- ggplot(plot_data, aes(x = cat_ordered, y = n, fill = income_group)) +
  geom_col(position = "dodge", alpha = 0.85, width = 0.9) +
  facet_wrap(~era, scales = "free_y", ncol = 1) +
  coord_flip() +
  scale_fill_manual(values = c(
    "High income" = "steelblue",
    "Upper middle income" = "steelblue4", 
    "Lower middle income" = "yellow3",
    "Low income" = "orange"
  )) +
  labs(title = "FIG 13: Top COVID Interventions by Era & Income Group",
       subtitle = "Global top-10 categories shown consistently",
       x = "Intervention Category", y = "# Registrations") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold"),
        axis.text.y = element_text(size = 10))

fig13_fixed

```

```{r}
# ── 6.1 IPD intent by era ─────────────────────────────────────────────────────
ipd_data <- study_table %>%
  filter(st_reg_id %in% cohort_ids) %>%
  count(era, plan_ipd_share_yn, name = "n_trials") %>%
  group_by(era) %>%
  mutate(pct = n_trials / sum(n_trials)) %>%
  ungroup()

# FIG 13: IPD intent trends
fig13_ipd <- ggplot(ipd_data, aes(x = era, y = pct, fill = plan_ipd_share_yn)) +
  geom_col(position = "fill", width = 0.75) + coord_flip()+
  geom_text(aes(label = paste0(n_trials, "\n(", percent(pct, accuracy = 1), ")")), 
            position = position_stack(vjust = 0.5),
            color = "white", fontface = "bold", size = 3.2) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = c(
    "yes" = "green4",      # Green
    "no" = "pink3",       # Red
    "no information provided" = "#95a5a6", # Grey
    "undecided" = "#95a5b3"  # Orange
  )) +
  labs(title = "FIG 13: IPD Sharing Intent by Registration Era",
       subtitle = "Counts (pct) shown | Cohort trials only",
       y = "Share of Trials") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 15, hjust = 1))

# ── 6.3 IPD by geography ─────────────────────────────────────────────────────
ipd_geo <- study_table %>%
  left_join(country_table %>% filter(country_slot_n == 1) %>% 
              select(st_reg_id, income_group),
            by = "st_reg_id") %>%
  filter(!is.na(income_group)) %>%
    count(income_group, plan_ipd_share_yn, name = "n_trials") %>%
  group_by(income_group) %>%
  mutate(pct = n_trials / sum(n_trials))

# FIG 14: IPD by income group
# ── FIG 14: IPD Intent by Income Group (HORIZONTAL BARS) ─────────────────────
fig14_ipd_horizontal <- ggplot(ipd_geo, 
                               aes(y = income_group, 
                                   x = pct, fill = plan_ipd_share_yn)) +
  geom_col(position = "stack", alpha = 0.85, width = 0.75) +
  geom_text(aes(label = paste0(n_trials, " (", percent(pct, accuracy = 1), ")")), 
            position = position_stack(vjust = 0.5),
            color = "white", fontface = "bold", size = 3.5)+
  scale_x_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.05))) +
  scale_fill_manual(values = c(
     "yes" = "green4",      # Green
    "no" = "pink3",       # Red
    "no information provided" = "#95a5a6", # Grey
    "undecided" = "#95a5b3", "NA"="lightgrey"            # Light grey
  )) +
  labs(title = "FIG 14: IPD Sharing Intent by Country Income Group",
       subtitle = "Counts (% within income group) | Primary country analysis",
       x = "Share of Trials", y = "World Bank Income Group") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 12),
    axis.text.y = element_text(size = 12, face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.5),
    plot.margin = margin(20, 40, 20, 20)
  ) +
  guides(fill = guide_legend(nrow = 1, title = "IPD Sharing Intent"))

fig14_ipd_horizontal


```

