---
title: "Clean 1 (QC / checking) — revised"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 5,
  dpi = 300,
  fig.align = "center",
  out.width = "100%"
)

# Core libs
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(scales)
})

theme_pub <- function(base_size = 12, base_family = "sans") {
  ggplot2::theme_minimal(base_size = base_size, base_family = base_family) +
    ggplot2::theme(
      plot.title.position = "plot",
      plot.title = element_text(face = "bold"),
      plot.subtitle = element_text(margin = margin(b = 6)),
      axis.title = element_text(face = "bold"),
      axis.text.x = element_text(angle = 45, hjust = 1),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      legend.title = element_text(face = "bold"),
      legend.position = "right"
    )
}
```


```{r helpers}
# Small helper for QC logging (safe if not present in downstream scripts)
report_step <- function(df_in, df_out, msg) {
  cat("\n\n---", msg, "---\n")
  cat("Rows in :", nrow(df_in), "\n")
  cat("Rows out:", nrow(df_out), "\n")
  invisible(df_out)
}
```


```{r original-clean1, echo=TRUE}
# ---- ORIGINAL CONTENT (unchanged) ----
## 1. Setup


library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(countrycode)
library(lubridate)

### 1.1 Load raw REDCap export

data <- read_csv("../data/raw/data_2402.csv")

trial_reference_list <- read_csv("../data/raw/trial_reference_list.csv")

# Standardise IDs in reference list upfront (lowercase, trimmed)
trial_reference_list <- trial_reference_list %>%
  mutate(st_reg_id = str_to_lower(str_trim(st_reg_id)))
```

## 2. Helper functions

```{r helpers, message=FALSE}
# Standard text cleaning (keeps NA as NA; makes values consistent for filtering)
clean_txt <- function(x) {
  x <- as.character(x)
  x <- str_replace_all(x, "\\s+", " ") |> str_trim() |> str_to_lower()
  x[x %in% c("", "na", "n/a", "unknown", "-99")] <- NA
  x
}

# REDCap-style yes/checked handling
is_yes <- function(x) {
  x <- clean_txt(x)
  x %in% c("yes", "y", "true", "1", "checked", "selected")
}

# Report how many rows removed at each filtering step
report_step <- function(prev_df, new_df, step_name) {
  prev_n <- nrow(prev_df)
  new_n  <- nrow(new_df)
  removed <- prev_n - new_n
  cat(sprintf("%-35s: removed %5d | remaining %5d\n", step_name, removed, new_n))
  invisible(new_df)
}

# Country cleaning (keeps original casing; avoids treating continents as NA by accident)
clean_country <- function(x) {
  x <- as.character(x)
  x <- str_replace_all(x, "\\s+", " ") |> str_trim()
  x <- na_if(x, "")
  x <- na_if(x, "-99")
  x <- na_if(x, "Unknown")
  x <- na_if(x, "UNKNOWN")
  x <- na_if(x, "NA")
  x <- na_if(x, "N/A")
  x
}

# Report how many rows removed at each filtering step
scount <- function(df, step_name) {
 n <- length(unique(df$st_reg_id))
  cat(sprintf("Unique studies in table %-35s: %5d " , step_name, n))
  invisible(df)
}
```

## 3. Study-level table

### 3.1 Extract study-level rows (non-repeating instrument rows) 

```{r study-extract}
study_table <- subset(data, is.na(data$redcap_repeat_instrument))
st_raw<-subset(data, is.na(data$redcap_repeat_instrument))
```

### 3.3 Apply study-level filtering (step-wise with counts)

**Data is all studies from DAG (Pharma RCTs)**
**study_table is the main table at study level** This will undergo filtering based on inclusion exclusion
1) Eligible
2) Not cancelled
3) Registered after March 2020
4) Pharmaceuticals only
5) RCTs (Prospective + Interventional)?


```{r study-filter}

# Clean all values to make filtering robust (lowercase, trim, NA handling)
st0 <- study_table %>%
  mutate(across(where(is.character), clean_txt))

cat(sprintf("%-35s: removed %5d | remaining %5d\n", "Start (cleaned)", 0, nrow(st0)))

# 0) Filter to only trial IDs present in trial_reference_list (de-duplicated trial IDs, do not contain multiple registrations of the same trial)
st_ref_ids <- trial_reference_list %>% distinct(st_reg_id)

st0 <- st0 %>% semi_join(st_ref_ids, by = "st_reg_id")
report_step(study_table, st0, "Filter to trial reference list")

# 1) Eligible = Yes
st1 <- st0 %>% filter(is_yes(st_elig_yn))
report_step(st0, st1, "Eligible = Yes")

# 2) Exclude cancelled (NA treated as not cancelled)
st2 <- st1 %>% filter(!is_yes(st_cancelled))
report_step(st1, st2, "Exclude cancelled")

# 3) Registered after March 2020
st3 <- st2 %>%
  mutate(reg_date = dmy(st_reg_date)) %>%
  filter(is.na(reg_date) | reg_date >= as.Date("2020-03-01"))
report_step(st2, st3, "Exclude before March 2020")

# Final study cohort
study_table <- st3
rm(st0, st1, st2, st3, st_ref_ids)

scount(study_table, "Study table")

```

```{r}
chk_studytype<-study_table %>% filter(st_retro_prosp=="retrospective"|st_type=="observational")
chk<-chk_studytype$st_reg_id
chk_studytype1<-st_raw %>% filter(str_to_lower(st_reg_id) %in% chk)
#write.csv(chk_studytype1,"../QC/study_designtype.csv")
rm(chk_studytype,chk_studytype1)
```


## 4. Study–Country table

### 4.1 Pivot country slots (st_ctry1_name … st_ctry7_name) to long format

```{r country-extract}
ctry_cols <- grep("^st_ctry\\d+_name$", names(study_table), value = TRUE)

if (!"st_reg_id" %in% names(study_table)) stop("st_reg_id not found in `study_table`.")
if (length(ctry_cols) == 0) warning("No st_ctry*_name columns found. Will rely on st_countries parsing only (not implemented here).")

country_long <- study_table %>%
  select(st_reg_id, all_of(ctry_cols)) %>%
  pivot_longer(
    cols = all_of(ctry_cols),
    names_to = "country_slot",
    values_to = "country_raw"
  ) %>%
  mutate(
    country_raw = clean_country(country_raw),
    country_slot_n = readr::parse_number(country_slot)
  ) %>%
  select(st_reg_id, country_raw, country_slot_n)

# Quick diagnostics
length(unique(country_long$st_reg_id))
table(is.na(country_long$country_raw))

# Trials where the first slot is missing (potentially need st_countries parsing later)
no_country <- filter(country_long, country_slot_n == 1 & is.na(country_raw))
chk<-no_country$st_reg_id
chk_nocountry<-st_raw %>% filter(str_to_lower(st_reg_id) %in% chk)
if (!dir.exists("../QC")) dir.create("../QC", recursive = TRUE)
write.csv(chk_nocountry,"../QC/no_country.csv")
rm(no_country)
rm(chk_nocountry)
```

### 4.2 Keep non-missing countries + standardise via countrycode
(not filtering the country_table with cohort_ids)

```{r country-standardise}
country_table <- country_long %>%
  filter(!(is.na(country_raw)&country_slot_n>1)) %>% #Remove pivot artifacts only (not missing countries
  distinct(st_reg_id, country_raw, .keep_all = TRUE) %>%
  arrange(st_reg_id, country_raw)

report_step(country_long,country_table, "Remove pivot artifacts only (not missing countries)")
length(unique(country_table$st_reg_id))

# Small normalisations (minimal change from your version)
country_table$country_raw <- gsub("asia (except japan)", "Asia", country_table$country_raw, fixed = TRUE)

country_table$country_code <- countrycode(country_table$country_raw, origin = "country.name", destination = "iso3c")
country_table$country_std  <- countryname(country_table$country_raw)

rm(country_long)
scount(country_table,"Country")
```

## 5. Arm-level table

### 5.1 Extract “Study Arm” repeating instrument rows

```{r arm-extract}

arm_raw <- data %>%
  filter(redcap_repeat_instrument == "Study Arm") %>%
  mutate(
    st_reg_id      = str_to_lower(str_trim(st_reg_id)),
    arm_id         = suppressWarnings(as.integer(redcap_repeat_instance)),
    across(where(is.character), clean_txt),
    sa_num_intv    = suppressWarnings(as.integer(sa_num_intv)),
    sa_num_planned = suppressWarnings(as.numeric(sa_num_planned))
  )

scount(arm_raw, "Arm raw")

```

### 5.3 Join study-level fields and compute arm planned N

```{r}


arm_tbl <- arm_raw %>%
  select(
    st_reg_id, redcap_repeat_instance, arm_id,
    sa_num_intv, sa_combi, sa_crossover, sa_num_planned,
    any_of(c(
      paste0("sa_intv", 1:10, "_target"),
      paste0("sa_intv", 1:10, "_med_type"),
      paste0("sa_intv", 1:10, "_drug_all"),
      paste0("sa_intv", 1:10, "_all"),
      paste0("sa_intv", 1:10, "_desc"),
      paste0("sa_intv", 1:10, "_atmp"),
      paste0("sa_intv", 1:10, "_drug_oth")
    ))
  ) %>%
  left_join(
    study_table %>% select(st_reg_id, st_reg_date, st_design, st_phase, st_sample, st_intv_arms),
    by = "st_reg_id"
  ) %>%
  mutate(
    st_sample     = suppressWarnings(as.numeric(st_sample)),
    st_intv_arms  = suppressWarnings(as.integer(st_intv_arms)),
    arm_n_planned = dplyr::coalesce(
      sa_num_planned,
      if_else(!is.na(st_sample) & !is.na(st_intv_arms) & st_intv_arms > 0,
              st_sample / st_intv_arms,
              as.numeric(NA))
    ),
    arm_n_source = case_when(
      !is.na(sa_num_planned)                                                                ~ "sa_num_planned",
      is.na(sa_num_planned) & !is.na(st_sample) & !is.na(st_intv_arms) & st_intv_arms > 0 ~ "st_sample/st_intv_arms",
      TRUE                                                                                   ~ NA_character_
    )
  )

arm_table <- arm_tbl %>%
  select(
    st_reg_id,
    arm_id = redcap_repeat_instance,
    st_reg_date, st_design, st_phase, st_sample, st_intv_arms,
    sa_num_intv, sa_combi, sa_crossover, sa_num_planned,
    arm_n_planned, arm_n_source,
    any_of(c(
      paste0("sa_intv", 1:10, "_target"),
      paste0("sa_intv", 1:10, "_med_type"),
      paste0("sa_intv", 1:10, "_drug_all"),
      paste0("sa_intv", 1:10, "_all"),
      paste0("sa_intv", 1:10, "_desc"),
      paste0("sa_intv", 1:10, "_atmp"),
      paste0("sa_intv", 1:10, "_drug_oth")
    ))
  )

arm_table %>% summarise(n_arms = n(), n_trials = n_distinct(st_reg_id))
scount(arm_table, "arm")

```


### 5.2 Arm level diagnostics

There are reg_ids in arm table that are not htere in study table and vice-a-versa

```{r}


# 1) Unique ID sets
ids_st_raw  <- st_raw        %>% distinct(st_reg_id)
cohort_ids  <- study_table   %>% distinct(st_reg_id)
ids_arm     <- arm_table     %>% distinct(st_reg_id)

# 2) Mismatch lists
ids_in_arm_not_in_cohort  <- ids_arm       %>% anti_join(cohort_ids, by = "st_reg_id")
ids_in_cohort_not_in_arm  <- cohort_ids    %>% anti_join(ids_arm,    by = "st_reg_id")

cat("Unique studies in RAW study rows:  ", nrow(ids_st_raw), "\n")
cat("Unique studies in STUDY COHORT:    ", nrow(cohort_ids), "\n")
cat("Unique studies with ARM rows:      ", nrow(ids_arm),    "\n\n")
cat("ARM present but NOT in cohort:     ", nrow(ids_in_arm_not_in_cohort), "\n")
cat("In cohort but NO arms:             ", nrow(ids_in_cohort_not_in_arm), "\n\n")
cat("Arm coverage among cohort studies: ",
    round(100 * (nrow(cohort_ids) - nrow(ids_in_cohort_not_in_arm)) / nrow(cohort_ids), 1),
    "%\n")

# 3) Audit WHY arm-present studies are not in cohort
study_flags <- st_raw %>%
  mutate(across(where(is.character), clean_txt)) %>%
  mutate(
    flag_eligible      = is_yes(st_elig_yn),
    flag_not_cancelled = !is_yes(st_cancelled),
    flag_interventional = is.na(st_type) | str_detect(st_type, "interventional"),
    flag_rct           = !is.na(st_design) & str_detect(st_design, "rct"),
    reg_date_parsed    = suppressWarnings(dmy(st_reg_date)),
    flag_year_2020     = is.na(reg_date_parsed) | reg_date_parsed >= as.Date("2020-03-01")
  ) %>%
  select(st_reg_id, starts_with("flag_"), reg_date_parsed, st_design, st_type, st_elig_yn, st_cancelled)

arm_not_in_cohort_audit <- ids_in_arm_not_in_cohort %>%
  left_join(study_flags, by = "st_reg_id") %>%
  mutate(
    exclusion_reason = case_when(
      is.na(flag_eligible)    ~ "missing flags / study row missing after cleaning",
      !flag_eligible          ~ "ineligible (st_elig_yn != yes)",
      !flag_not_cancelled     ~ "cancelled",
      !flag_interventional    ~ "not interventional (st_type)",
      !flag_rct               ~ "not RCT (st_design)",
      !flag_year_2020         ~ "registered before 03-2020",
      TRUE                    ~ "passes these flags — check other filters"
    )
  )

arm_not_in_cohort_audit %>% count(exclusion_reason, sort = TRUE)

```
```{r}
rm( arm_not_in_cohort_audit, arm_raw,arm_tbl,                     ids_arm,        ids_in_arm_not_in_cohort,ids_in_cohort_not_in_arm,
ids_st_raw,st_raw,study_flags )
```

```
