---
title: "Clean 2 (Standardisation / QC) — revised"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 5,
  dpi = 300,
  fig.align = "center",
  out.width = "100%"
)

# Core libs
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(scales)
})

theme_pub <- function(base_size = 12, base_family = "sans") {
  ggplot2::theme_minimal(base_size = base_size, base_family = base_family) +
    ggplot2::theme(
      plot.title.position = "plot",
      plot.title = element_text(face = "bold"),
      plot.subtitle = element_text(margin = margin(b = 6)),
      axis.title = element_text(face = "bold"),
      axis.text.x = element_text(angle = 45, hjust = 1),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      legend.title = element_text(face = "bold"),
      legend.position = "right"
    )
}
```


```{r helpers}
clean_txt <- function(x) {
  x %>%
    as.character() %>%
    stringr::str_squish() %>%
    stringr::str_to_lower()
}
```


# ---- ORIGINAL CONTENT (mostly unchanged) ----


* Fixes the **missing object** issue (`component-role-missingness-qc` → `component_role_missingness_qc`)
* Makes the intervention logic **explicit and testable** (placebo/SOC empties are expected)
* Ensures **alignment to your master cohort**: interventions are restricted to `study_table$st_reg_id` (so you don’t accidentally analyse arms from trials that didn’t pass study filters)
* Produces two analysis-ready tables you’ll re-use everywhere:

  * `arm_drug_table` (arm–drug)
  * `study_drug_table` (study–drug)

## 1. Setup

```{r setup, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)

# A stable master ID set (use this to align ALL downstream tables)
master_ids <- unique(study_table$st_reg_id)

## 2. Helper checks (minimal)


n_study <- length(master_ids)
n_arm   <- length(unique(arm_table$st_reg_id))

cat("Unique studies in study_table:", n_study, "\n")
cat("Unique studies in arm_table  :", n_arm, "\n")

# Reg_ids present in arms but not in filtered study cohort
arm_not_in_study <- setdiff(unique(arm_table$st_reg_id), master_ids)
study_not_in_arm <- setdiff(master_ids, unique(arm_table$st_reg_id))

cat("Reg_ids in arm_table but NOT in study_table:", length(arm_not_in_study), "\n")
cat("Reg_ids in study_table but NOT in arm_table:", length(study_not_in_arm), "\n")
```

## 3. Align arms to the study cohort

**Why we do this:**
Your `study_table` is the “source of truth” cohort (eligible, not cancelled, etc.).
So for analysis we **semi-join** arms to the master cohort.
We still keep a QC list (`arm_not_in_study`) if you want to inspect what got excluded later.

```{r align-arms-to-study, message=FALSE, warning=FALSE}
arm_table_aligned <- arm_table %>%
  semi_join(study_table %>% select(st_reg_id), by = "st_reg_id")

cat("Arms after aligning to study cohort:\n")
print(arm_table_aligned %>% summarise(n_arms = n(),
                                     n_trials = n_distinct(st_reg_id)))

```

## 4. Build a component-level table (arm × component-slot)

**Why we do this:**
In your REDCap export, interventions are stored as up to 3 component slots per arm:

* `sa_intv1_*`, `sa_intv2_*`, `sa_intv3_*`

To analyse interventions consistently, we pivot those slots long, giving:

* **1 row = 1 arm-component slot**

This makes it easy to classify placebo vs pharmacological vs SOC.


```{r component-table-build, message=FALSE, warning=FALSE}

# Safety check: confirm at least intv1 core columns exist
needed_cols <- c("sa_intv1_target", "sa_intv1_med_type", "sa_intv1_drug_all")
missing_cols <- setdiff(needed_cols, names(arm_table_aligned))
if (length(missing_cols) > 0) stop("Missing expected intervention columns: ", paste(missing_cols, collapse = ", "))

# Show which intv slots are actually present (useful for QC)
intv_cols_present <- grep("^sa_intv([1-9]|10)_", names(arm_table_aligned), value = TRUE)
cat("Intervention columns found in arm_table_aligned:\n")
print(intv_cols_present)

# Pivot all 7 sub-fields across intv1–10
component_table <- arm_table_aligned %>%
  pivot_longer(
    cols         = matches("^sa_intv([1-9]|10)_(target|med_type|drug_all|all|desc|atmp|drug_oth)$"),
    names_to     = c("component_index", ".value"),
    names_pattern = "^sa_intv([1-9]|10)_(target|med_type|drug_all|all|desc|atmp|drug_oth)$"
  ) %>%
  mutate(
    component_index = as.integer(component_index),
    target    = clean_txt(target),
    med_type  = clean_txt(med_type),
    drug_all  = clean_txt(drug_all),
    atmp      = clean_txt(atmp),
    drug_oth  = clean_txt(drug_oth)
  )

# Quick size check before any dropping
cat("Component table (pre-cleaning):\n")
print(component_table %>% summarise(
  n_rows       = n(),
  n_trials     = n_distinct(st_reg_id),
  n_arms       = n_distinct(st_reg_id, arm_id),
  n_slots_1to3 = sum(component_index <= 3),
  n_slots_4to10 = sum(component_index >= 4)
))

# Quick look at missingness per sub-field (to inform blank-dropping decision later)
cat("\nMissingness per sub-field:\n")
component_table %>%
  summarise(across(c(target, med_type, drug_all, all, desc, atmp, drug_oth),
                   ~ mean(is.na(.)))) %>%
  print()

```


```{r component-table-drop-blanks, message=FALSE, warning=FALSE}

component_table_clean <- component_table %>%
  mutate(
    is_blank_slot = is.na(target) & is.na(med_type) & is.na(drug_all) & 
                    is.na(all) & is.na(desc)
  ) %>%
  filter(!is_blank_slot) %>%
  select(-is_blank_slot)

cat("Component table after dropping blank slots:\n")
print(component_table_clean %>% summarise(
  n_rows        = n(),
  n_trials      = n_distinct(st_reg_id),
  n_arms        = n_distinct(st_reg_id, arm_id),
  n_slots_1to3  = sum(component_index <= 3),
  n_slots_4to10 = sum(component_index >= 4)
))

# Sanity check: how many rows were dropped
cat("\nRows dropped as blank pivot artifacts:", nrow(component_table) - nrow(component_table_clean), "\n")
cat("Rows retained:                        ", nrow(component_table_clean), "\n")

```
```{r}
# Keep only pharmacological + ATMP components
component_table_clean <- component_table_clean %>%
  filter(target %in% c(
    "pharmacological interventions",
    "advanced therapy medicinal products (atmp)"
  ))

cat("After restricting to pharma + ATMP targets:\n")
print(component_table_clean %>% summarise(
  n_rows   = n(),
  n_trials = n_distinct(st_reg_id),
  n_arms   = n_distinct(st_reg_id, arm_id)
))

# Optional: check target counts to confirm
print(table(component_table_clean$target))


component_table_clean <- component_table_clean %>%
  mutate(
    drug_std = case_when(
      !is.na(drug_all) ~ drug_all,
      target == "advanced therapy medicinal products (atmp)" ~ atmp,
      TRUE ~ NA_character_
    )
  )

# QC: how many still missing after this rule?
component_table_clean %>%
  summarise(
    n_rows        = n(),
    n_missing_std = sum(is.na(drug_std))
  ) %>%
  print()

```



```{r}
chk<-component_table_clean %>% filter(is.na(drug_std))
unresolved_199 <- chk %>% 
  mutate(id = row_number())


corrections <- read_csv("C:/Users/rchhajed/OneDrive - Nexus365/Tropical Medicine - IDDO - COVID19/COVID19 LMR 2025/Cov_Main/data/drug_others_std.csv")
View(corrections)

# 3. Join corrections onto the unresolved rows
unresolved_199_joined <-  left_join( unresolved_199 ,corrections %>% select(id, drug_std_extracted),  by = "id")


# Join extracted values back to FULL component_table_clean
component_table_clean1 <- component_table_clean %>%
  left_join(
    unresolved_199_joined %>% 
      select(st_reg_id, arm_id, component_index, drug_std_extracted),
    by = c("st_reg_id", "arm_id", "component_index")
  )

# Check it worked (should show 199 rows with extracted values)
component_table_clean1 %>%
  filter(is.na(drug_std)) %>%  # original missing rows
  count(is.na(drug_std_extracted)) %>%
  print()


component_table_clean1 <- component_table_clean1 %>%
  mutate(
    drug_std = coalesce(drug_std, drug_std_extracted))

component_table_clean1 %>%
  summarise(
    n_rows        = n(),
    n_missing_std = sum(is.na(drug_std)),
    n_pharma      = sum(target == "pharmacological interventions"),
    n_atmp        = sum(target == "advanced therapy medicinal products (atmp)")
  ) %>%
  print()
```

```{r}
component_table_clean2 <- component_table_clean1 %>%
  mutate(
    # --- Clean drug_std → drug_std_cleaned (light formatting only) ---
    drug_std_cleaned = drug_std %>%
      str_to_lower() %>%
      str_replace_all("\\(.*?\\)", " ") %>%               # remove parentheses notes
      str_replace_all("[^a-z0-9\\+\\/\\-\\,\\s]", " ") %>% # keep separators
      str_replace_all("\\s+", " ") %>%
      str_trim() %>%
      na_if(""),  # empty strings → NA
      
    # --- Apply synonym harmonisation → drug_std2 ---
    drug_std2 = case_when(
      # Painkillers
      str_detect(drug_std_cleaned, "acetaminophen|paracetamol") ~ "paracetamol",
      
      # Zinc variants
      str_detect(drug_std_cleaned, "zinc\\s*(sulphate|chloride|citrate)?") ~ "zinc (any salt)",
      
      # Anticoagulants
      str_detect(drug_std_cleaned, "enoxaparin") ~ "enoxaparin",
      
      # Antivirals/cough
      str_detect(drug_std_cleaned, "bromhexine") ~ "bromhexine",
      
      # Saline
      str_detect(drug_std_cleaned, "saline") ~ "saline",
      
      # Typos
      drug_std_cleaned == "leflunoide" ~ "leflunomide",
      
      # Monoclonals
      str_detect(drug_std_cleaned, "monoclonal\\s*antibod") ~ "monoclonal antibody (unspecified)",
      
      # Protease inhibitors
      str_detect(drug_std_cleaned, "protease inhibitor") ~ "protease inhibitor (unspecified)",
      
      # Default: keep original
      TRUE ~ drug_std_cleaned
    )
  ) %>%
  select(-drug_std_cleaned)  # drop intermediate

# QC: compare before/after
component_table_clean2 %>%
  filter(!is.na(drug_std)) %>%
  count(drug_std, drug_std2) %>%
  filter(drug_std != drug_std2) %>%
  print(n = 50)




# STAGE 1: Clean drug_std (raw → cleaned name)
# ============================================================
component_table_clean2 <- component_table_clean2 %>%
  mutate(
    drug_std2 = case_when(
      # --- Previously confirmed fixes ---
      drug_std2 == "others"                            ~ "other",
      drug_std2 == "antipyretics"                      ~ "antipyretic",
      drug_std2 == "anti-tussive"                      ~ "antitussives",
      drug_std2 == "anticoagulants"                    ~ "anticoagulation",
      drug_std2 == "anti-coagulant"                    ~ "anticoagulation",
      drug_std2 == "local anaesthetic"                 ~ "anaesthetic",
      drug_std2 == "adamumab"                          ~ "adalimumab",
      drug_std2 == "leflunomide"                       ~ "leflunoide",
      drug_std2 == "camostat mesylat"                  ~ "camostat mesilate",
      drug_std2 == "lipoic acid"                       ~ "alpha-lipoic acid",
      drug_std2== "protease inhibitor (unspecified)"  ~ "protease inhibitors unknown/not on list",
      drug_std2 == "monoclonal antibody (unspecified)" ~ "monoclonal antibodies unknown/not on list",
      drug_std2 == "icatibant acetate"                 ~ "icatibant",
      drug_std2 == "leukine"                           ~ "sargramostim",
      drug_std2 == "vitamin b complex"                 ~ "vitamin b",
      drug_std2 == "vitamin super b-complex"           ~ "vitamin b",
      TRUE ~ drug_std2
    )
  )




```

```{r}
library(readr)
drug_labels<-read_csv("C:/Users/rchhajed/OneDrive - Nexus365/Tropical Medicine - IDDO - COVID19/COVID19 LMR 2025/Cov_Main/data/drug_labels.csv", 
    col_types = cols(med_type_old = col_skip(), 
        med_type = col_skip()))

# 2. Clean column names and select the useful ones
drug_labels <- drug_labels %>%
    select(drug_std, broad_cat, drug_class, label, who_status) %>%
  # Handle duplicates: keep the row with non-NA broad_cat (most complete)
  group_by(drug_std) %>%
  slice_head(n = 1) %>%  # first occurrence if tie
  ungroup() %>%
  filter(!is.na(drug_std))  # drop any blank drug_std2

component_table_clean2$drug_std_old<-component_table_clean2$drug_std
component_table_clean2$drug_std<-component_table_clean2$drug_std2
component_table_clean2$drug_all<-NULL
component_table_clean2$drug_std2<-NULL
# 3. Join to your main table
component_table_clean3 <- component_table_clean2 %>%
  left_join(
    drug_labels,
    by = "drug_std"
  )

# 4. QC: join success rate
component_table_clean3 %>%
  summarise(
    n_rows_total     = n(),
    n_with_labels    = sum(!is.na(broad_cat)),
    n_with_class     = sum(!is.na(drug_class)),
    n_with_label     = sum(!is.na(label)),
    n_join_success   = sum(!is.na(broad_cat) | !is.na(drug_class) | !is.na(label))
  ) %>%
  print()

# 5. Show top 10 drugs with labels
component_table_clean3 %>%
  filter(!is.na(broad_cat)) %>%
  count(drug_std, broad_cat, sort = TRUE) %>%
  head(10) %>%
  print()
```
Current drug columns:

drug_all          # raw source
drug_oth          # raw fallback  
desc              # raw messy text
atmp              # raw ATMP source  
drug_std          # rule-based + extracted  
drug_std_extracted # manual corrections
drug_std_old      # ? (seems redundant)

```{r}
library(readr)
library(dplyr)

# 1. Load the new assignments CSV
new_labels <-  read_csv("C:/Users/rchhajed/OneDrive - Nexus365/Tropical Medicine - IDDO - COVID19/COVID19 LMR 2025/Cov_Main/data/drug_labels_new_assignments.csv") %>%
  select(drug_std, broad_cat, drug_class, label) # keep only needed columns


# 2. Fill in missing broad_cat/drug_class/label using new assignments
component_table_clean4 <- component_table_clean3 %>%
  left_join(
    new_labels,
    by = "drug_std",
    suffix = c("", "_new")   # new columns get _new suffix
  ) %>%
  mutate(
    # Fill only where original join left NAs
    broad_cat  = coalesce(broad_cat,  broad_cat_new),
    drug_class = coalesce(drug_class, drug_class_new),
    label      = coalesce(label,      label_new)
  ) %>%
  select(-broad_cat_new, -drug_class_new, -label_new)  # drop temp columns

# 3. QC: how many still missing after both joins?
component_table_clean4 %>%
  summarise(
    n_total         = n(),
    n_with_labels   = sum(!is.na(broad_cat)),
    n_still_missing = sum(is.na(broad_cat))
  ) %>%
  print()

# 4. Check what is still missing
component_table_clean4 %>%
  filter(is.na(broad_cat)) %>%
  count(drug_std, sort = TRUE) %>%
  print(n = 20)

```
```{r}
pharma_table<- component_table_clean4 %>%
  select(
    # --- Trial identifiers ---
    st_reg_id, arm_id, component_index,

    # --- Trial-level descriptors ---
    st_reg_date, st_design, st_phase, st_sample, st_intv_arms,

    # --- Arm-level descriptors ---
    sa_num_intv, sa_combi, sa_crossover, sa_num_planned,
    arm_n_planned, arm_n_source,

    # --- Intervention classification ---
    target, med_type,

    # --- Final drug columns only ---
    drug_std,           # final cleaned drug name
    broad_cat,          # high-level category
    drug_class,         # specific class
    label,              # human-readable label
    who_status          # WHO trial status
  )

```


## 12. Save key tables (optional but recommended)
```{r}
pharma_table <- pharma_table %>%
  mutate(drug_std = case_when(

    # Sofosbuvir — registry typo
    drug_std == "sofusbovir"                        ~ "sofosbuvir",
    drug_std == "sofosbovir"                        ~ "sofosbuvir",

    # Vitamin D: D, D3, and cholecalciferol are the same compound
    drug_std %in% c("vitamin d3",
                    "cholecalciferol",
                    "vitamin d3 (cholecalciferol)") ~ "vitamin d",

    # Lopinavir/ritonavir: DO NOT merge into one row here.
    # They appear as separate arm components in your table.
    # They will be visually co-located on figures via broad_cat = "Antivirals"
    # and flagged as a combination pair in the Methods note.

    # Hydroxychloroquine vs chloroquine: KEEP SEPARATE.
    # Different compounds; chloroquine is more toxic and was quickly abandoned.
    # Merging would obscure that story.

    TRUE ~ drug_std
  ))


# ── STEP 3: Handle "corticosteroids" catch-all ───────────────────────────────
# These are entries where the registrant did not specify which corticosteroid.
# They are genuine unknowns — do NOT merge with dexamethasone/methylprednisolone.
# Rename for clarity so they are distinguishable in figures.

pharma_table <- pharma_table %>%
  mutate(drug_std = if_else(drug_std == "corticosteroids",
                            "corticosteroids (unspecified)",
                            drug_std))


# ── STEP 4: Enforce correct broad_cat for all drugs ──────────────────────────

```


```{r}

library(readxl)
wb_country <- read_excel("C:/Users/rchhajed/OneDrive - Nexus365/Tropical Medicine - IDDO - COVID19/COVID19 LMR 2025/Cov_Main/data/wb_country.xlsx")

wb_country  <- wb_country  %>% rename(country_code = Code)
wb_country  <- wb_country  %>% rename(income_group = `Income group`)

country_table<-left_join(country_table,wb_country[,c("country_code","income_group")],by='country_code')
```

```{r}
 

# ── OPTION 1: Load purrr (simplest if you already use tidyverse) ──────────────
library(purrr)

# ── OPTION 2: Replace map_lgl with base R sapply — no extra package needed ───
# Change this line:
#   filter(map_lgl(drugs_in_arm, ~ "ritonavir" %in% .)) 
# To this:
#   filter(sapply(drugs_in_arm, function(x) "ritonavir" %in% x))

# ── Full corrected block ──────────────────────────────────────────────────────
arm_drug_combos <- pharma_table %>%
  group_by(st_reg_id, arm_id) %>%
  summarise(
    drugs_in_arm     = list(unique(drug_std)),
    has_lopinavir    = "lopinavir"  %in% drug_std,
    has_nirmatrelvir = any(str_detect(drug_std, "nirmatrelvir|pf-07321332")),
    has_atazanavir   = "atazanavir" %in% drug_std,
    .groups = "drop"
  )

ritonavir_recode <- arm_drug_combos %>%
  filter(sapply(drugs_in_arm, function(x) "ritonavir" %in% x)) %>%   # <-- fixed
  mutate(ritonavir_label = case_when(
    has_lopinavir    ~ "lopinavir/ritonavir",
    has_nirmatrelvir ~ "nirmatrelvir/ritonavir",
    has_atazanavir   ~ "atazanavir/ritonavir",
    TRUE             ~ "ritonavir (boosted, unspecified)"
  )) %>%
  select(st_reg_id, arm_id, ritonavir_label)

# Apply recode to ritonavir rows
pharma_table <- pharma_table %>%
  left_join(ritonavir_recode, by = c("st_reg_id", "arm_id")) %>%
  mutate(drug_std = if_else(
    drug_std == "ritonavir" & !is.na(ritonavir_label),
    ritonavir_label,
    drug_std
  )) %>%
  select(-ritonavir_label)

# Apply same recode to lopinavir rows in the same arms
pharma_table <- pharma_table %>%
  left_join(ritonavir_recode, by = c("st_reg_id", "arm_id")) %>%
  mutate(drug_std = case_when(
    drug_std == "lopinavir" & ritonavir_label == "lopinavir/ritonavir" 
      ~ "lopinavir/ritonavir",
    TRUE ~ drug_std
  )) %>%
  select(-ritonavir_label)

# QC
pharma_table %>%
  filter(str_detect(drug_std, "ritonavir|lopinavir")) %>%
  count(drug_std, sort = TRUE)
pharma_table <- pharma_table %>%
  mutate(broad_cat_display = case_when(
    str_detect(broad_cat, "^Antivirals")           ~ "Antivirals",
    str_detect(broad_cat, "^Immunotherapies")      ~ broad_cat,  # keep granular
    str_detect(broad_cat, "^Anti.inflammatories")  ~ "Anti-inflammatories",
    TRUE                                           ~ broad_cat
  ))


pharma_table <- pharma_table %>%
  mutate(display_group = case_when(

    # ── 1. ANTIMALARIALS ──────────────────────────────────────────────────────
    label == "Antimalarials"                                        ~ "Antimalarials",

    # ── 2. ANTIVIRALS (REPURPOSED) ────────────────────────────────────────────
    label == "Antivirals (Antiretrovirals)"                         ~ "Antivirals (repurposed)",
    label == "Antivirals (Broad-spectrum/Other)"                    ~ "Antivirals (repurposed)",
    label == "Immunotherapy (Innate/Other)" &
      drug_std %in% c("interferons", "interferon beta -1a")         ~ "Antivirals (repurposed)",

    # ── 3. ANTIVIRALS (DIRECT-ACTING) ─────────────────────────────────────────
    label == "Antivirals (Direct-acting)"                           ~ "Antivirals (direct-acting)",

    # ── 4. CORTICOSTEROIDS ────────────────────────────────────────────────────
    label %in% c("Corticosteroids (Systemic)",
                 "Corticosteroids (Inhaled)")                       ~ "Corticosteroids",

    # ── 5. IMMUNOMODULATORS ───────────────────────────────────────────────────
    label %in% c("Immunotherapy (IL-6 blockers)",
                 "Immunotherapy (JAK inhibitors)",
                 "Immunotherapy (Other kinases)",
                 "Immunotherapy (BTK inhibitors)",
                 "Immunotherapy (Small molecule)",
                 "Immunotherapy (Other biologics)", "Immunotherapies (other immunomodulators")                 ~ "Immunomodulators",

    # ── 6. ANTIBODY THERAPIES ─────────────────────────────────────────────────
    label %in% c("Immunotherapy (Anti-spike mAbs)",
                 "Immunotherapy (Conv. Plasma)")                    ~ "Antibody Therapies",

    # ── 7. ANTICOAGULANTS ─────────────────────────────────────────────────────
    label %in% c("Anticoagulants (Heparins)",
                 "Anticoagulants (Non-heparin)")                    ~ "Anticoagulants",

    # ── 8. ANTI-INFLAMMATORIES ────────────────────────────────────────────────
    label %in% c("Anti-inflammatories (Non-NSAID)",
                 "Anti-inflammatories (NSAIDs)")                    ~ "Anti-inflammatories",

    # ── 9. ANTIPARASITICS ─────────────────────────────────────────────────────
    label == "Antiparasitics"                                       ~ "Antiparasitics",

    # ── 10. METABOLIC AGENTS ──────────────────────────────────────────────────
    label %in% c("Metabolic agents (Statins)",
                 "Metabolic agents (SGLT-2 inhibitors)",
                 "Metabolic agents (Insulin-sensitizing)",
                 "Metabolic agents (Other)")                        ~ "Metabolic agents",

    # ── 11. SUPPORTIVE CARE ───────────────────────────────────────────────────
    label %in% c("Vitamins & Supplements",
                 "Respiratory/Hemodynamic Support",
                 "Other Supportive Care")                           ~ "Supportive Care",

    # ── 12. OTHER/UNSPECIFIED — kept separate, filter out before plotting ──────
    label == "Other/Uncategorized"                                  ~ "Other/Unspecified",
    label == "Immunotherapy (Innate/Other)"                         ~ "Other/Unspecified",
    label == "Anti-depressants"                                     ~ "Other/Unspecified",
    is.na(label)                                                    ~ "Other/Unspecified",
    TRUE                                                  ~ "Other/Unspecified"  ))


```

```{r}

cohort <- study_table 
cohort_ids <- cohort %>% distinct(st_reg_id)


pharma_in_cohort <- pharma_table %>%
  semi_join(cohort_ids, by = "st_reg_id")



# If your pharma_table already has drug_std and med_type cleaned, use them directly:
study_drug <- pharma_in_cohort %>%
  filter(!is.na(drug_std), drug_std != "") %>% 
  distinct(st_reg_id, drug_std, .keep_all = TRUE) 


# Ensure st_sample numeric (used in Figure 4 summaries)
study_drug <- study_drug %>%
  mutate(st_sample = suppressWarnings(as.numeric(st_sample))) %>% 
   filter(!drug_std == "antibiotics") 

# Quick coverage
c(
  n_studies_in_cohort      = n_distinct(cohort$st_reg_id),
  n_studies_with_any_drug  = n_distinct(study_drug$st_reg_id),
  n_unique_drugs           = n_distinct(study_drug$drug_std)
)

study_drug_filtered<- study_drug %>% filter(!drug_std=="other")

drugcat_plot <- study_drug_filtered %>%
  mutate(
    reg_date  = as.Date(st_reg_date, format = "%d/%m/%Y"),
    reg_year  = year(reg_date),
    reg_month = month(reg_date),

    time_period = case_when(
      reg_year == 2020 & reg_month <= 3  ~ "2020 Q1",
      reg_year == 2020 & reg_month <= 6  ~ "2020 Q2",
      reg_year == 2020 & reg_month <= 9  ~ "2020 Q3",
      reg_year == 2020 & reg_month <= 12 ~ "2020 Q4",
      reg_year == 2021 & reg_month <= 3  ~ "2021 Q1",
      reg_year == 2021 & reg_month <= 6  ~ "2021 Q2",
      reg_year == 2021 & reg_month <= 9  ~ "2021 Q3",
      reg_year == 2021 & reg_month <= 12 ~ "2021 Q4",
      reg_year == 2022 & reg_month <= 6  ~ "2022 H1",
      reg_year == 2022 & reg_month <= 12 ~ "2022 H2",
      reg_year == 2023                   ~ "2023",
      reg_year %in% c(2024, 2025)        ~ "2024–25",
      TRUE                               ~ NA_character_
    ),

    time_period = factor(time_period, levels = c(
      "2020 Q1", "2020 Q2", "2020 Q3", "2020 Q4",
      "2021 Q1", "2021 Q2", "2021 Q3", "2021 Q4",
      "2022 H1", "2022 H2",
      "2023",
      "2024–25"
    ))
  )
```



**Why we do this:**
So later analysis chunks don’t depend on re-running everything.
```{r}
## 12. Save Clean2 outputs as .RData

# Choose an output folder (edit as needed)
out_dir <- "C:/Users/rchhajed/OneDrive - Nexus365/Tropical Medicine - IDDO - COVID19/COVID19 LMR 2025/Cov_Main/data"
if (!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)

# Filename with date stamp (optional)
rdata_file <- file.path(out_dir, paste0("covid_lmr_clean5_", format(Sys.Date(), "%Y%m%d"), ".RData"))

# Save only key objects (keeps workspace clean + reproducible)
save(
  study_table,          # from Clean1
  country_table,        # from Clean1 (if you created it)
  arm_table,            # from Clean1
  pharma_table, study_drug,drugcat_plot,
  file = rdata_file
)

cat("Saved Clean2 objects to:\n", rdata_file, "\n")
```
```
