

# --- PART 2: Sample Size Preparation (Section 3) ---
```{r}
cohort_ss <- cohort %>%
  mutate(
    # Convert sample size to numeric
    st_sample_n = suppressWarnings(as.numeric(st_sample)),
    
    # Ensure date is Date object
    reg_date = as.Date(reg_date),
    
    # Quarter Date (for reference)
    reg_qdate = floor_date(reg_date, "quarter"),
    
    # Pretty Quarter Label
    time_window = paste0("Q", quarter(reg_date), " ", year(reg_date)),
    
    # Half-Year Label (H1/H2)
    half_year = case_when(
      is.na(reg_date) ~ NA_character_,
      month(reg_date) <= 6 ~ paste0("H1 ", year(reg_date)),
      TRUE ~ paste0("H2 ", year(reg_date))
    )
  )

# Define Half-Year Levels chronologically
# This ensures the plot order is correct (H1 2020, H2 2020, etc.)
half_levels <- cohort_ss %>%
  filter(!is.na(reg_date)) %>%
  distinct(reg_date, half_year) %>%
  arrange(reg_date) %>%
  pull(half_year) %>%
  unique()

cohort_ss$half_year <- factor(cohort_ss$half_year, levels = half_levels)

# QC Check
cohort_ss %>%
  summarise(
    n_studies = n_distinct(st_reg_id),
    pct_sample_missing = mean(is.na(st_sample_n))
  )


```


#Section 3  Sample size distribution and trends
3.0 Prep: derive time windows + numeric planned sample size
Why: sample size is stored as character sometimes; convert once.
Why time windows: required for stratified distribution plots.

```{r}
cohort_ss <- cohort %>%
  mutate(
    st_sample_n = suppressWarnings(as.numeric(st_sample)),
    
    reg_date = as.Date(reg_date),
    
    # Quarter date
    reg_qdate = floor_date(reg_date, "quarter"),
    
    # Pretty label like "Q1 2020"
    time_window = paste0(
      "Q", quarter(reg_qdate), " ", year(reg_qdate)),
    
    half_year = case_when(
      is.na(reg_date) ~ NA_character_,
      month(reg_date) <= 6 ~ paste0("H1 ", year(reg_date)),
      TRUE ~ paste0("H2 ", year(reg_date)))
    
  )

# Order chronologically
quarter_levels <- cohort_ss %>%
  distinct(reg_qdate, time_window) %>%
  arrange(reg_qdate) %>%
  pull( time_window)

cohort_ss$time_window <- factor(
  cohort_ss$time_window,
  levels = quarter_levels
)

# Order chronologically
half_levels <- cohort_ss %>%
  distinct(reg_qdate, half_year) %>%
  arrange(reg_qdate) %>%
  pull( half_year)

cohort_ss$half_year <- factor(
  cohort_ss$half_year,
  levels = unique(half_levels))


# QC
cohort_ss %>%
  summarise(
    n_studies = n_distinct(st_reg_id),
    pct_sample_missing = mean(is.na(st_sample_n))
  )

```
##Figure 6A — Overall sample size distribution

What it shows: how fragmented vs scaled the trial landscape is, overall.
```{r}


## Figure 6A table ----
# Why: use numeric sample sizes only; keep NAs out of distribution computations.
fig6_overall <- cohort_ss %>%
  filter(!is.na(st_sample_n)) %>%
  select(st_reg_id, st_sample_n, reg_date, time_window)


```
##Figure 6B — Sample size distribution by time window

What it shows: whether median/IQR moved over time (bigger, better-powered trials vs persistent small trials).,

```{r}

fig6_by_time <- cohort_ss %>%
  filter(!is.na(st_sample_n), !time_window=="QNA NA") %>%
  select(st_reg_id, st_sample_n, time_window, half_year)


#Figure 6 summary table (medians/IQR) to report in text
## Summary stats for reporting ----
fig6_stats <- cohort_ss %>%
  filter(!time_window=="QNA NA") %>% 
  group_by(half_year) %>%
  summarise(
    n_studies = n_distinct(st_reg_id),
    n_with_sample = sum(!is.na(st_sample_n)),
    median = median(st_sample_n, na.rm = TRUE),
    q1 = quantile(st_sample_n, 0.25, na.rm = TRUE),
    q3 = quantile(st_sample_n, 0.75, na.rm = TRUE),
    
    .groups = "drop"
  )

fig6_stats

p6b <- ggplot(fig6_by_time, aes(x = half_year, y = st_sample_n)) +
  annotation_logticks(sides = "l", linewidth = 0.4, color = "#999999") + 
  geom_violin(fill = "#f0f8ff", alpha = 0.6, color = "white", linewidth = 0.3, width = 0.85) +
  geom_boxplot(fill = "#1f77b4", alpha = 0.7, width = 0.55, 
               outlier.color = "#ff7f00", outlier.alpha = 0.7, outlier.size = 1.1) +
  
  # Labels: Q1 (left/blue), Median (center/white), Q3 (right/blue)
  geom_text(data = fig6_stats, aes(x = half_year, y = q1, label = comma(round(q1))), 
            nudge_x = -0.15, nudge_y = -0.1, size = 3, color = "#2E86C1", fontface = "bold") +
  geom_text(data = fig6_stats, aes(x = half_year, y = q3, label = comma(round(q3))), 
            nudge_x = 0.2, nudge_y = 0.08, size = 3, color = "#2E86C1", fontface = "bold") +
  geom_text(data = fig6_stats, aes(x = half_year, y = median, label = comma(round(median))), 
            nudge_x = 0, nudge_y = 0.1, size = 3, color = "#FFFFFF", fontface = "bold") +
  
  scale_y_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 10000, 50000),
    labels = scales::comma_format(accuracy = 1)
  ) +
  scale_x_discrete(expand = expansion(add = c(0.3, 0.5))) +
  labs(
    title = "Figure 6B. Planned sample size evolution by time window",
    subtitle = "Violin = density; Q1/Median/Q3 labeled; log10 scale",
    x = NULL,
    y = "Planned sample size (log10)"
  ) +
  theme_plotly_static(base_size = 11) +
  theme(
    axis.text.x = element_text(angle = 35, hjust = 1, vjust = 1, size = 9),
    axis.text.y = element_text(size = 9),
    panel.grid.major.y = element_line(color = "#E1E5E9", linewidth = 0.6),
    plot.subtitle = element_text(size = 10, color = "#666666", face = "italic"),
    plot.title = element_text(margin = margin(b = 10))
  )

ggsave("fig6b_publication.png", p6b, width = 12, height = 8, dpi = 300, bg = "white")
p6b



```



##Figure 6C — Sample size distribution by intervention pre/post 2022
```{r}
library(tidyverse)
library(scales)
library(lubridate)

fig6c_data <- fig6c_data %>%
  group_by(display_group, phase) %>%
  mutate(n_in_group = n()) %>%
  ungroup()

ggplot(fig6c_data,
       aes(x      = st_sample,
           y      = display_group,
           fill   = phase,
           colour = phase)) +

  geom_vline(xintercept = 100,
             linetype = "dotted",
             colour   = "red",
             linewidth = 0.7) +
  annotate("text", x = 105, y = "Supportive Care",  # use actual factor level not 0.5
           label = "N = 100", hjust = 0,
           colour = "red", size = 2.8) +

  geom_boxplot(
   data = ~filter(., n_in_group >= 10),
   aes(fill = phase),
    position      = position_dodge(width = 0.7),
    width         = 0.55,
    outlier.size  = 0.5,
    outlier.alpha = 0.3,
    #colour        = "white",
    linewidth     = 0.4,
    alpha         = 0.85
  ) +

  stat_summary(
    aes(fill = phase),
    fun      = median,
    geom     = "point",
    shape    = 21,
    size     = 2.5,
    colour   = "grey20",
    position = position_dodge(width = 0.7)
  ) +

  geom_text(
    data = fig6c_counts,
    aes(x = 50000, y = display_group,
        label = paste0("n=", n_trials),
        colour = phase),
    position    = position_dodge(width = 0.7),
    hjust       = 1, size = 2.4,
    inherit.aes = FALSE,
    show.legend = FALSE
  ) +

  # ── ADD THIS LINE — overrides theme_pub's scale_y_continuous ──
  scale_y_discrete() +

  scale_x_log10(
    breaks = c(10, 50, 100, 500, 1000, 5000, 50000),
    labels = c("10", "50", "100", "500", "1k", "5k", "50k"),
    expand = expansion(mult = c(0.02, 0.05))
  ) +
  scale_fill_manual(
    values = c("Pandemic (2020–2022)" = "#0077BB",
               "Endemic (2023–2025)"  = "#EE7733"),
    name = NULL
  ) +
  scale_colour_manual(
    values = c("Pandemic (2020–2022)" = "#0077BB",
               "Endemic (2023–2025)"  = "#EE7733"),
    name = NULL
  ) +

  labs(
    title    = "Figure 6C. Planned sample size by intervention category and phase",
    subtitle = "Log scale  |  Red line = N 100  |  Dot = median  |  Box = IQR",
    x        = "Planned sample size (log scale)",
    y        = NULL
  ) +
  theme_pub(base_size = 11) +
  theme(
    legend.position      = "top",
    legend.justification = "left",
    panel.grid.major.y   = element_line(colour = "grey92", linewidth = 0.4),
    axis.text.y          = element_text(size = 9)
  ) +
  geom_jitter(
  data = ~filter(., n_in_group < 10),
  aes(colour = phase),
  width = 0, height = 0.15,
  size = 2, alpha = 0.7
)


```
